|

### 2021-04-11 appendix/appendix.Rmd
revised appendix

We complemented this by doing a term search on Google Scholar after having finished the entire eligibility procedure on the first sample. We formulated the search string based on the terms and expressions that appeared most commonly in the articles included in our meta-analysis. The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending. The search string was as follows: *(“upper chamber size” OR "lower chamber size" OR “council size” OR “parliament size” OR “legislature size” OR “number of legislators” OR “legislative size") AND (“spending” OR “expenditure" OR “government size”)*. We scraped Google Scholar on March 5th, 2021. Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously. We then performed the exact same eligibility procedures, further explained below. This resulted in 3,041 additional records.

@@

```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]

  \footnotesize
  \linespread{1.0}

@@

@@

In this section, we show the descriptive statistics for our sample. We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.

@@

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.

@@

```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=6, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients", y = '') +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors", y = '') +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal. The descriptive statistics for the moderators are available below.

@@

Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

@@

@@

@@

The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary indicator for electoral system.

@@

Therefore, we find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita. Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

## Log Lower House Size and Expenditure per Capita

@@

```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

@@

@@

The forest plot follows below:

```{r, echo = FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

@@

The forest plot follows below:

@@

@@

@@

@@

@@

@@

@@

```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

Therefore, we see that majoritarian systems do not have a clear positive effect on budgetary spending. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

@@

```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

```{r, fig.width=8, fig.height=6, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

>>>>

We complemented this by doing a term search on Google Scholar after having finished the entire eligibility procedure on the first sample. We formulated the search string based on the terms and expressions that appeared most commonly in the articles included in our meta-analysis. The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending. The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`. We scraped Google Scholar on March 5th, 2021. Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously. We then performed the exact same eligibility procedures, further explained below. This resulted in 3,041 additional records.

@@

```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}

@@

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 10)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 3)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
```

@@

Here we show the descriptive statistics for our sample. We focus on the following paper characteristics: study year; paper publication; the  electoral system mentioned in the publication; and the distribution of the dependent and independent variables of interest.

@@

The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.

@@

```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) +
    geom_bar(color = "black") +
  labs(x = "Published Study?",
       y = "") +
  theme_bw()
```

@@

```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2,
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") +
  labs(x = "",
       y = "Dependent Variables") +
  coord_flip() +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") +
  labs(x = "Coefficients", y = '') +
  theme_bw()
```

@@

```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") +
  labs(x = "Standard Errors", y = '') +
  theme_bw()
```

@@

We chose a set of moderators that frequently appear in the literature and may help us interpret our results. We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$). The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal.

@@

Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign. The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Thus, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.

@@

The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita is available below.

@@

```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary indicator for electoral system. The results may be seen below.

We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita. Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

@@

## Log of Lower House Size and Expenditure per Capita

@@

```{r, fig.width=7, fig.height=3, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
build_forest(mod, NULL)
```

We see no evidence of publication bias:

```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

The funnel plot shows no evidence of publication bias.

@@

```{r, fig.width=8, fig.height=10, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot:

@@

The funnel plot to test for publication bias:

@@

```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
build_forest(mod, NULL)
```

The funnel plot is available below:

@@

@@

As in our previous estimations, we find no evidence of file-drawer effect.

@@

Here we estimate a meta-analysis of the papers which use instrumental variables. The results may be seen below.

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

No evidence of publication bias, as shown in the following tunnel plot:

@@

In this subsection, we run a meta-analysis with papers that include regression discontinuity designs.

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

We see that majoritarian systems do not have a clear positive effect on budgetary spending. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.

```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
                 capt = NULL, hetvar = aux$elecsys2)
```

@@

```{r, fig.width=9, fig.height=10, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

The funnel plot suggests no publication bias.

@@

```{r, fig.width=8, fig.height=7, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And the funnel plot:

```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=8, fig.height=7, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And here is the funnel plot to assess the possibility of publication bias:

```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod)
```

@@

```{r, fig.width=8, fig.height=5, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

And the funnel plot:
